Meta-analysis of composite outcomes in clinical trials

### 2025-06-13 MSc_poster_template.Rmd
Trying to fix merge issues

poster_height: "594mm"
poster_width: "841mm"
column_numbers: 5
column_margins: "0.5in"	
primary_colour:	"#a80050"	# Secondary colour use for poster design.
secondary_colour:	"#84003d"	# Main colour used for poster design.
accent_colour:	"#e6007e"	# A third colour option.
author_textcol: "white"
title_textsize: "80pt"
author_textsize: "60pt"
body_textsize: "25pt"
output: 
  posterdown::posterdown_html:
    self_contained: true
    pandoc_args: --mathjax
    number_sections: false
knit: pagedown::chrome_print
---

@@

```{r}

@@

EMERGE_background_stats <- data.frame(t(as.matrix(EMERGE_background_stats)))
knitr::kable(EMERGE_background_stats, caption = 'EMERGE *p*-values', align = 'c', format = "html") %>%
  kable_styling(font_size = 20) %>%
  add_header_above(c("Primary Composite Outcome N/total (%)" = 2, " " = 1))
```
# Analysis of EMERGE DATA SET
The primary composite outcome at 32 and 38 weeks was not significantly different between the **metformin group (154 of 264) and the placebo group (82 of 262)**. This lack of significance is indicated by a **risk difference of -6.9%** (95% CI, -15.1% to 1.4%) and a**relative risk of 0.89** (95% CI, 0.78 to 1.02).

@@

####

@@

# Create a binary column for Insulin
tmpDat$binary_insulin <- 0
tmpDat$binary_insulin[tmpDat$InsulinYN == "Yes"] <- 1

# Proportion test for Insulin usage between groups
StudyInsulinTest <- prop.test(
  x = c(
    sum(tmpDat$InsulinYN[tmpDat$Group == "Metformin"] == "Yes", na.rm = TRUE),
    sum(tmpDat$InsulinYN[tmpDat$Group == "Placebo"] == "Yes", na.rm = TRUE)
  ),
  n = c(
    sum(tmpDat$Group == "Metformin"),
    sum(tmpDat$Group == "Placebo")
  )
)

@@

# Calculate composite scores
y_squared_composite <- (insulin_t$statistic^2) + (gw32_t$statistic^2) + (gw38_t$statistic^2)
study_non_squared_composite <- insulin_t$statistic + gw32_t$statistic + gw38_t$statistic

# Visualization: Proportion of Insulin Usage by Group
ggplot(tmpDat, aes(x = Group, fill = InsulinYN)) +
  geom_bar(position = "fill") +
  labs(
    title = "Proportion of Insulin Usage by Group",
    y = "Proportion",
    x = "Group"
  ) +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal()

# Visualization: Boxplots for gw32 and gw38 with cutoff line at 5.1 and p-values
ggplot(tmpDat, aes(x = Group, y = gw32, fill = Group)) +
  geom_boxplot() +
  geom_hline(yintercept = 5.1, linetype = "dashed", color = "red") +
  annotate("text", x = 1.5, y = max(tmpDat$gw32, na.rm = TRUE), 
           label = paste("p-value:", round(gw32_t$p.value, 4)), 
           color = "blue", size = 4) +
  labs(
    title = "Gestational Week 32 by Group",
    y = "Week 32",
    x = "Group",
    caption = "Dashed red line represents the cutoff at 5.1"
  ) +
  theme_minimal()

ggplot(tmpDat, aes(x = Group, y = gw38, fill = Group)) +
  geom_boxplot() +
  geom_hline(yintercept = 5.1, linetype = "dashed", color = "red") +
  annotate("text", x = 1.5, y = max(tmpDat$gw38, na.rm = TRUE), 
           label = paste("p-value:", round(gw38_t$p.value, 4)), 
           color = "blue", size = 4) +
  labs(
    title = "Gestational Week 38 by Group",
    y = "Week 38",
    x = "Group",
    caption = "Dashed red line represents the cutoff at 5.1"
  ) +
  theme_minimal()

@@

ggplot(correlation_melted, aes(Var1, Var2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2)), color = "white") +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0) +
  labs(
    title = "Correlation Matrix (Pearson)",
    x = "Variables",
    y = "Variables"
  ) +
  theme_minimal()

@@

```{r morefigs2, out.width='95%', echo=FALSE, fig.cap='Power of Permutation Test', fig.height=4.5}

>>>>

poster_height: "594mm"
poster_width: "841mm"
column_numbers: 4
column_margins: "0.5in"	
primary_colour:	"#a80050"	# Secondary colour use for poster design.
secondary_colour:	"#84003d"	# Main colour used for poster design.
accent_colour:	"#e6007e"	# A third colour option.
author_textcol: "white"
title_textsize: "80pt"
author_textsize: "60pt"
body_textsize: "25pt"
output: 
  posterdown::posterdown_html:
    self_contained: true
    pandoc_args: --mathjax
    number_sections: false
knit: pagedown::chrome_print
---

@@

```{r mytable, out.width='80%'}

@@

EMERGE_background_stats <- data.frame(t(as.matrix(EMERGE_background_stats)))
styled_caption <- "<span style='font-family: Arial; font-size: 18px; font-weight: bold; color: black;'>Summary of Primary Composite in EMERGE</span>"
knitr::kable(EMERGE_background_stats, caption = styled_caption, align = 'c', format = "html") %>%
  kable_styling(font_size = 20) %>%
  add_header_above(c("Primary Composite Outcome N/total (%)" = 2, " " = 1))
```

@@

#### 
# Descriptive Statistics of Datasets

@@

@@

# Visualization: Boxplots for gw32 and gw38 with cutoff line at 5.1 and p-values
ggplot(tmpDat, aes(x = Group, y = gw32, fill = Group)) +
  geom_boxplot() +
  geom_hline(yintercept = 5.1, linetype = "dashed", color = "red") +
  annotate("text", x = 1.5, y = max(tmpDat$gw32, na.rm = TRUE), 
           label = paste("p-value:", round(gw32_t$p.value, 4)), 
           color = "blue", size = 4) +
  labs(
    title = "Gestational Week 32 by Group",
    y = "Week 32",
    x = "Group"
  ) +
  theme_minimal()+
  theme(axis.title = element_text( size = 24),
        axis.text = element_text(size = 18),
        plot.title = element_text(size = 28))

ggplot(tmpDat, aes(x = Group, y = gw38, fill = Group)) +
  geom_boxplot() +
  geom_hline(yintercept = 5.1, linetype = "dashed", color = "red") +
  annotate("text", x = 1.5, y = max(tmpDat$gw38, na.rm = TRUE), 
           label = paste("p-value:", round(gw38_t$p.value, 4)), 
           color = "blue", size = 4) +
  labs(
    title = "Gestational Week 38 by Group",
    y = "Week 38",
    x = "Group"
  ) +
  theme_minimal()+
  theme(axis.title = element_text( size = 24),
        axis.text = element_text(size = 18),
        plot.title = element_text(size = 28))

@@

ggplot(correlation_melted, aes(Var1, Var2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = round(value, 2)), color = "white") +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0) +
  labs(
    title = "Correlation Matrix (Pearson)",
    x = "Variables",
    y = "Variables"
  ) +
  theme_minimal()+
  theme(axis.title = element_text( size = 24),
        axis.text = element_text(size = 18),
        plot.title = element_text(size = 28))

@@

```{r morefigs2, out.width='95%', echo=FALSE, fig.cap='Power of Permutation Test', fig.height=4}
